%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    {\Huge\scshape Jessica Horton} \\ \vspace{3pt}
    \small
    \hspace{.5pt}{Data Analyst}
    $|$
    \hspace{.5pt}{Interdisciplinary Physicist}
    $|$
    \hspace{.5pt}{Scientific Programmer} \\ \vspace{1.5pt}
    \faMobile  \hspace{.5pt} \href{tel:12345678900}{+1 234 - 567 - 8900}
    $|$
    \faEnvelope \hspace{.5pt} \href{mailto:email@gmail.com}{email@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/jjessicahorton}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/jjessicahorton}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Boone,+NC/@36.2083704,-81.7045677,13z/data=!3m1!4b1!4m6!3m5!1s0x8850d12869945a65:0x6e0a346179f5a6e9!8m2!3d36.2181951!4d-81.6830378!16zL20vMDFmeGw?entry=ttu&g_ep=EgoyMDI2MDIyNS4wIKXMDSoASAFQAw%3D%3D}{Boone, NC}
\end{center}



%-----------PROFESSIONAL SUMMARY-----------

\section{Professional Summary}
  \vspace{3pt}
  \begin{center}
    Recent Physics graduate with interdisciplinary training in chemistry, mathematics, and computational data analysis. Extensive understanding
    of real-world applications of Ordinary, Partial, and Higher Order Differential Equations, Dynamical Systems, Statistical Modeling, Fourier Analysis, 
    and Linear Algebra, computationally, theoretically, and experimentally. Proficient in complex problem solving, identifying areas of interdisciplinary overlap,
    scientific programming, experimental design, data analysis and visualization, and rapidly adapting
    to new learning opportunities. Experience working in a Neuroscience lab, Organic and Biochemistry Lab, Circuits lab, and Optics lab. 
    Seeking employment in engineering, data analytics, or research which require modeling and simulation opportunities applied to challenging physical systems, or
    other pertinent real-world problems.

% Recent Physics graduate and soon-to-be published author with an Interdisciplinary focus in Chemistry, Mathematics, and Neuroscience.
% Extensive understanding of real-world applications of Ordinary, Partial, and Higher Order Differential Equations, Dynamical Systems,
% Statistical Modeling, Fourier Analysis, and Linear Algebra, both computationally and theoretically. Proficient in complex problem
% solving, identifying areas of interdisciplinary overlap, scientific programming, writing and conducting experiments, data analysis
% and visualization, effective scientific communication, and rapidly adapting to new learning opportunities. Experience working
% in a Neuroscience lab, Organic and Biochemistry Lab, Circuits lab, and Optics lab. Looking for job opportunities which require complex
% problem-solving with respect to pertinent real-world issues.
% 
% Physics graduate with interdisciplinary training in chemistry, mathematics, and computational data analysis. 
% Experienced in scientific programming, statistical modeling, experimental design, and quantitative problem‑solving 
% across laboratory and computational environments. Demonstrated ability to analyze complex datasets, build 
% computational models, and communicate technical results clearly. Seeking an engineering, data analysis, or 
% research role where strong analytical skills and physics-based problem solving can contribute to 
% aerospace technologies and advanced systems.

% Physics graduate with interdisciplinary training in chemistry and mathematics and experience in computational modeling, 
% data analysis, and experimental physics. Strong background in differential equations, statistical modeling, Fourier analysis,
%  and scientific computing applied to complex physical systems. Experienced in Python-based data analysis, quantitative modeling, 
%  experimental design, and technical communication. Seeking to apply analytical problem solving and modeling & simulation skills 
% to engineering challenges in advanced aerospace systems.

% Key words to highlight:
% - quantitative analysis (appeared twice)
% - computational analysis
% - data analysis
% - data visualization
% - statistical analysis
% - statistical modeling
% - Engineering analysis
% - computational modeling
% - mathematical modeling
% - modeling and simulation
% - experimental systems
% - experimental physics (appeared twice)
% - computational physics
% - complex problem solving
% - analytical problem solving
% - scientific research
% - experimental physics
% - computational modeling
% - optics and signal processing
% - Physics-based modeling
% - Applied Physics
% - Physical systems analysis
% - Signal analysis
% - Image processing? (we know signal processing is important)
% - Quantitative image analysis
% - Microscopy Imaging
% - Experimental data aquisition, visualization, and analysis
% - Thermodynamics
% - Aerodynamics


  \end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading{Appalachian State University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Boone, NC}{B.Sc. in Physics, Interdisciplinary Sciences}{August 2021 \textbf{--} December 2025}{Minors in Chemistry and Mathematics}{Spring 2022 \textbf{--} December 2025}
  \resumeSubHeadingListEnd



  
%----------- Publications -----------

\section{Publications}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{The RNA-binding protein Pumilio limits polymodal nociception in \emph{Drosophila} larvae}}{}
          \resumeItemListStart
            \resumeItem{This manuscript-in-revision details the findings extracted from the Python-based statistical analysis performed and the data visualizations created on multiple sets of data experimentally collected by colleagues.}
            % \resumeItem{This manuscript-in-revision details the findings which outline that the Pumilio RNA-binding protein acts to limit nociceptive sensitivity by way of its activity in nociceptive sensory neurons, and that in order for larvae to be capable of expressing nociceptive sensitization following an injury, Pumilio must be found in the nociceptors.}
            % \resumeItem{I earned my co-authorship on this paper through the statistical analysis I performed the data collected via Python.}
            \resumeItem{This project required different sets of data to be compared using analytical tools such as Cliff's Delta, the Permutation T Test, Mean and Median Difference Analysis, alongside creating a variety of different plots.}
            \resumeItemListEnd
      
    \resumeSubHeadingListEnd

    

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards}
      \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
              {\textbf{Appalachian State University}}{}
        % {\textbf{Appalachain State's College of Arts and Sciences Senior Spotlight Award}}{}
          \resumeItemListStart
          % \resumeItem{College of Arts and Sciences Senior Spotlight Award}
            % \resumeItem{In my last semester of my undergraduate degree, I was nominated for the Appalachian State College of Arts and Sciences Senior Spotlight Award by four of my mentors; the Executive Director of the College of Arts and Sciences, Ms. Diana Nelson, the Department Chair of the Department of Physics and Astronomy, Dr. Tonya Coffey, the Assistant Department Chair of the Department of Physics and Astronomy, Dr. Brooke Hester, and the Assistant Department Chair of the Department of Biology, Dr. Andy Bellemer.}
            \resumeItem{\href{https://cas.appstate.edu/news/cas-senior-spotlight-jess-horton}{\color{blue}College of Arts and Sciences Senior Spotlight Award}}
            \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Relevant Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages and Software:}{ Python, R, MATLAB, Mathematica, Maple, Anaconda, ImageJ, OpenCV, Catmaid, Flywire's Connectome in Codex} \\ \vspace{3pt}

        \textbf{Python Programming Packages:}{ pip, conda, NumPy, Pandas, Matplotlib, Seaborn, SciPy, Scikit-learn, dabest, statistics, Plotly, navis} \\ \vspace{3pt}

        \textbf{R Programming Packages:}{ tidyverse, ggplot2, tidymodels, natverse (nat, nat.nblast, nat.templatebrains)} \\ \vspace{3pt}
        
        \textbf{Mathematical Modeling and Simulation Tools:}{ Linear Algebra, Vector Calculus,  Ordinary Differential Equations, Partial Differential Equations, Higher Order Differential Equations, Dynamical Systems, Fourier Analysis, 
        Calculus of Variations, Bifurcation Analysis} \\ \vspace{3pt}

        \textbf{Experimental and Laboratory Skills:}{ Scientific Programming, Data Acquisition and Visualization, Statistical Analysis, Microscopy Imaging, Image Processing, Instrumentation and Equipment Calibration, Metrology, Error Analysis} \\ \vspace{3pt}

        \textbf{Scientific Communication:}{ Technical Writing, Presentation Skills, Literature Review, Data Verification and Validation} \\ \vspace{3pt}
                
    }}

    % Skill keywords to highlight:
    % - keywords used above
    % (everything below is Programmatic and related to Data Analysis, Modeling, and Simulation)
    % - Python
    % - MATLAB
    % - Scientific computing
    % - Data analysis 
    % - Data visualization
    % - Data processing
    % - Large Data Set Analysis
    % - Statistical analysis
    % - Numerical methods (do I have experience with that?)
    % - Computational modeling
    % - Statistical modeling
    % - Algorithm development
    % - Scientific programming
    %
    % (Mathematics and Modeling)
    % - Ordinary Differential Equations
    % - Partial Differential Equations
    % - Higher Order Differential Equations
    % - Dynamical Systems
    % - Fourier Analysis
    % - Linear Algebra
    % - Dynamical Systems
    % - Optimization Methods
    % - Predictive Modeling
    % - System Modeling
    % 


  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      % Reminder: Update GitHub Links
      
      \resumeProjectHeading
        {\textbf{Understanding Thermal Nociception Behavior: Analysis of the \emph{Drosophila} Connectome} $|$ \emph{\href{https://github.com/jjessicahorton/thermal-nociception-connectome}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Created brain maps which were computationally generated using Python and specialized Python macro packages, in which the neurological pathways involved in pain processing were systematically modeled, analyzed and visualized.}
            \resumeItem{The brain map visualizations were programmatically generated in Python, and sought to model and analyze the network of first-order input, output, and reciprocal neurons connected to neurons which possessed the neuropeptide, Allatostatin C.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{An Investigation of the Anticonvulsant Properties of Long Polyunsaturated Fatty Acids for 
        ...}}{}
          \resumeItemListStart
            \resumeItem{This research project investigated the molecular mechanisms by which long polyunsaturated fatty acids reduced seizure severity of para [bss1] flies, 
            which utilized seizure recovery times as the primary mode of measurement regarding the extent of severity.}
            \resumeItem{Personal contributions to this project consisted of managing the statistical and quantitative analysis of the data, which evaluated the outcomes for male and female flies with homozygous 
            and heterozygous para [bss1] mutations when seizure recovery assays were collected on them.} % using different types of fly food, including food infused with long polyunsaturated fatty acids.}
            % arachidonic acid-infused food and vehicle controlled food.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{A Quantitative and Qualitative Analysis of an Experimentally Determined Fast Fourier Transform}}{}
          \resumeItemListStart
            \resumeItem{Designed and conducted a Fourier Optics optical signal processing experiment, which used a 4F optical system to experimentally determine the Fast Fourier Transform of a beam of light.}
            %  used a four F's optics apparatus to experimentally measure the Fast Fourier Transform of a beam of light.}
            \resumeItem{By passing the beam first through a single slit, and then through two different lenses, a ThorLabs camera was used to capture images of 
            both the Fast Fourier Transform and the Inverse Fast Fourier Transform of the beam.}
            \resumeItem{ImageJ was then used to process all of the images and their associated data, and likewise process the images of the Inverse Fast Fourier Transform. As a result, the experimentally
            collected FFT and the computationally obtained Fast Fourier Transform (FFT) were quantitatively and qualitatively compared.}
            \resumeItem{From there, data related to the wave behavior of each image was graphically obtained and analyzed, such that the percent difference of each set of 
            data could be quantitatively and qualitatively assessed.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Experimentally Determining the Wavelength of Light}}{}
          \resumeItemListStart
            \resumeItem{Conducted an experiment that required the calculation of the wavelength of light for two different lasers, one of which was 
            blue, and another which was red.}
            \resumeItem{Two different diffraction grating lenses were utilized to diffract the light, and the right triangle created by the first order diffraction grating pattern 
            was used to calculate the wavelength of light for each laser.}
            % AI generated vvv
            \resumeItem{The percent difference of both the experimentally obtained and the computationally obtained wavelength was calculated, and the results were quantitatively analyzed.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://biology.appstate.edu/directory/dr-andrew-bellemer}{\color{blue}Dr. Andy Bellemer's} Cellular and Molecular Neuroscience Lab}{Boone, NC}
      {Undergraduate Research Assistant}{August 2022 \textbf{--} December 2025}
        \resumeItemListStart
            \resumeItem{Analyze, visualize, and communicate data related to multiple different projects throughout the lab using Python, Excel, and other platforms as needed clearly, concisely, and thoroughly.}
            \resumeItem{Create brain maps of a model organism in Python in order to visualize neurological pathways involved in pain processing.}
            \resumeItem{Engage in rigorous self study via review of online documentation for computational projects, staying up-to-date on the relevant literature, and filling in the gaps between undergraduate course load and the work performed in the lab.}
            \resumeItem{Engage in standardized and shared experimental, cleaning, and lab maintenance procedures required to uphold an efficient workflow.}
            \resumeItem{Practice and uphold laboratory safety standards, including properly managing bio-hazardous materials and chemical waste.}
        \resumeItemListEnd

    \resumeSubheading
      {UNC Health Appalachian}{Boone, NC}
      {Internal Medicine and Pulmonology Medical Assistant}{February 2025 \textbf{--} November 2025}
        \resumeItemListStart
            \resumeItem{Collect and document patient vitals alongside other important clinical data in order to prepare them for provider evaluation.}
            \resumeItem{Coordinate patient care workflow in a high-volume practice by communicating with patients, providers, and other medical staff to ensure that patients are seen in a timely manner.}
            \resumeItem{Utilized Epic's electronic medical record (EMR) system in order to document patient encounters, refill medications, update medical histories, and communicate with patients via MyChart.}
            \resumeItem{Perform diagnostic laboratory tests (COVID-19, influenza, streptococcal screening, urinalysis, glucose monitoring etc.) in-office, and report all results to providers.}
            \resumeItem{Administer intramuscular vaccinations and medications under provider supervision.}
            \resumeItem{Manage sensitive patient medical equipment, such as wheelchairs and oxygen tanks, effectively and safely.}
            \resumeItem{Uphold a sterile clinical environment, and safely dispose of biohazardous materials.}
        \resumeItemListEnd

    % \resumeSubheading
      % {Scale AI}{San Francisco, California, United States (Remote)}
      % {Prompt Engineer}{Mar 2023 \textbf{--} Sep 2023, Freelance}
        % \resumeItemListStart
            % \resumeItem{Crafted elaborate Turkish prompts for various generative AI tasks. Tailored prompts using well-defined formats such as natural language questions and structured inputs based on the task's domain to fine-tune the LLM, improving the chatbot's responses and enhancing overall performance.}
            % \resumeItem{Provided user feedback by reviewing and scoring the chatbot's responses to ensure they align with intended chatbot behaviors and the chatbot produces accurate and contextually appropriate responses to given prompts.}
            % \resumeItem{Engaged in collaborative meetings with cross-functional teams and project coordinators, actively seeking guidance, addressing queries, and collectively brainstorming strategies to generate higher-quality prompts.}
        % \resumeItemListEnd

    % \resumeSubheading
     %  {Max Planck Institute for Intelligent Systems}{Stuttgart, Baden\textbf{-}Württemberg, Germany}
     %  {Undergraduate Researcher}{Jun 2022 \textbf{--} Aug 2022, Internship}
      %   \resumeItemListStart
      %       \resumeItem{Engaged in collaborative research within the Robotics, Collectives and Learning subgroup at the Physical Intelligence Department with Ph.D. students \href{https://www.linkedin.com/in/sinan-ozgun-demir-981311129/}{\color{blue}Sinan Özgün Demir} and \href{https://www.linkedin.com/in/alpkaracakol/}{\color{blue}Alp Can Karacakol} on a project about 3D printing and heat-assisted magnetic programming of soft machines under the supervision of \href{https://www.linkedin.com/in/metin-sitti-0a8a712/}{\color{blue}Prof. Dr. Metin Sitti}.}
      %       \resumeItem{Optimized a C++ ROS package for real-time conversion of 3D motion controller events to ROS messages, achieving high-frequency and buffer-free synchronization.}
      %       \resumeItem{Developed an Arduino Mega driver to activate a laser and pressure regulator, for monitoring coil temperatures and PID tuning to control the coil currents. Established a robust ROS-Arduino communication network by integrating ROSSerial and handshaking to simulate a 3D printing and magnetic programming process with Python.}
            % \resumeItem{Designed the project's system and software architecture, flowchart, and state machine diagram. Expanded G-code capabilities by incorporating spherical coordinates to specify the direction of magnetization for shape morphing.}
      %   \resumeItemListEnd
    
    % \resumeSubheading
      % {Nanonetworking Research Group, Boğaziçi University}{Istanbul, Turkey}
      % {Undergraduate Researcher}{Oct 2021 \textbf{--} Jun 2022, Part-time}
        % \resumeItemListStart
            % \resumeItem{Worked on the “Design and Implementation of Molecular Communication Systems Using Index Modulation” project under the supervision of \href{https://www.linkedin.com/in/alipusane/}{\color{blue}Prof. Dr. Ali Emre Pusane}.}
            % \resumeItem{Simulated the Brownian motion of molecules in a SISO MCvD system and predicted simulation parameters such as receiver radius, diffusion coefficient, and transmitter-receiver distance using CNNs with Keras and TensorFlow.}
            % \resumeItem{Plotted the arrival of molecules per symbol duration in a SISO MCvD system using Binomial, Poisson, and Gaussian model approximations with MATLAB.}
            % \resumeItem{Ran Monte Carlo simulations of the Gaussian model to encode and decode randomized binary sequences in a SISO MCvD system using BCSK modulation technique and calculated the bit error rate on Z-channel.}
        % \resumeItemListEnd

    % \vspace{20pt}
    % \resumeSubheading
    %   {SESTEK Speech Enabled Software Technologies}{Istanbul, Turkey}
    %   {AI Research and Development Intern}{Jan 2022 \textbf{--} Feb 2022, Internship}
    %     \resumeItemListStart
    %         % \resumeItem{Executed diverse NLP tasks, including NER, POS tagging, sentiment analysis, text classification, and extractive and generative QA using transformers and Hugging Face libraries. Conducted a thorough literature review on information retrieval and reading comprehension to stay updated on SOTA ML models.}
    %         \resumeItem{Developed a generative QA system with dense passage retrieval (DPR) and retrieval-augmented generation (RAG) techniques using the Haystack framework and PyTorch.}
    %         \resumeItem{Worked on a Turkish open-domain QA system made by fine-tuning BERTurk and XLM-Roberta models. Tabularized exact match and F1 scores derived from DeepMind's XQuAD and various Turkish data sets.}
    %     \resumeItemListEnd

    % \resumeSubheading
      % {Meteksan Defense Industry Inc.}{Ankara, Turkey}
      % {Analog Design Engineering Intern}{Jul 2021 \textbf{--} Aug 2021, Internship}
        % \resumeItemListStart
            % \resumeItem{Designed and simulated numerous analog circuits such as voltage-mode controlled buck converter, phase-shifted full-bridge isolated DC-DC converter, and EMI filters with LTspice. Integrated these circuits and implemented a 320 W power distribution unit to be used in a radar system's power circuit board.}
            % \resumeItem{Researched real-world compatible electronic components to be used in such circuits including GaNFETs, high-side gate drivers, and Schottky diodes.}
            % \resumeItem{Assembled PCBs of both common and differential mode filters and used VNA Bode 100 to measure the cut-off frequencies.}
        % \resumeItemListEnd
    
  \resumeSubHeadingListEnd




%----------- AWARDS & ACHIEVEMENTS -----------

% \section{Technical Interests}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University. (Jul 2023)} \\ \vspace{3pt}
% 
%         \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK). (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}
%     
%         % \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)} \\ \vspace{3pt}
%         
%         \textbf{KYK Outstanding Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK). (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
%         
%         % \textbf{Boğaziçi University Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
%         
%         \textbf{Kocaeli Science High School Valedictorian Award:}{ Graduated as the highest ranked student. (Jun 2018)}
%     }}
%   \resumeSubHeadingListEnd




%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
